How did local health infrastructure and socio-political factors within different states and counties in the United States affect the disparities in COVID-19 outcomes, and what lessons can be learned for more targeted public health preparedness and response strategies in future pandemics?

### 2024-02-10 outputs/paper/paper.qmd
added references

The datasets utilized throughout this paper was obtained from the original paper.

@@

>>>>

The datasets utilized throughout this paper was obtained from the `original paper` [@citearticle].

@@

`R` [@citeR] was the language and enviroment used for the bulk of this analysis, alongside `tidyverse` [@citeTidyVerse], `sf` [@citeSF], `readxl` [@citeReadXL], `knitr` [@citeKnitR], `janitor` [@citeJanitor], `lubridate` [@citeLubridate], `dplyr` [@citeDplyr], `data.table` [@citeDataTable], `RColorBrewer` [@citeRColorBrewer], `ggpubr` [@citeggpubr], `ggplot2` [@citeggplot], `here` [@citeHere], and `scales` [@citeScales].
